Contracts for Contracts

### 2023-06-06 paper/background.tex
challenges

\paragraph{Challenges}
The unique features of the Solidity language and blockchain computation impose
several challenges that demand us exploring different design choices.
Here we summarize these challenges and in the next section we introduce the
design of \lang.

\begin{itemize}
  \item Rich higher-order computation:
    address are \emph{opaque first-class values carrying higher-order computation}.
  \item Distributed execution model
  \item Open-world assumption: unknown/adversarial caller, we do not know all the programs
    and cannot modify them
  \item Efficiency requirement: gas consumption
\end{itemize}

>>>>

\paragraph{Challenges}
Here we identify some major challenges imposed by the unique features of the
Solidity language and blockchain computation:

\begin{itemize}
  \item Rich higher-order computation:
    e.g., address are \emph{opaque first-class values carrying higher-order
    computation}.
  \item Distributed execution model:
    contracts are deployed on the blockchain and invoked remotely by an unknown
    or adversarial party.
  \item Open-world assumption:
    we do not have access and control of all smart contract programs.
  \item Efficiency requirement:
    deployed smart contract programs consumes ``gas'' and it is desirable
    to minimize gas consumption.
\end{itemize}

These challenges make it impossible to monitor all communication channels,
which further demands us exploring different design choices when layering
a specification and runtime monitoring system for Solidity.
